---
title: "update_ctca_analysis"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
#Load packages
library(tidyverse)
library(readr)
library(metafor)
library(meta)
library(readxl)
library(grid)
library(tidyr)
library(flextable)
library(boot)
library(epikit)
library(rmarkdown)
```

#Prevalence of coronary plaque

```{r, warning=FALSE, echo = FALSE}
#Begin Cleaning pipe chain
##########################

#Load excel file
ct <- read_excel("hiv_sr_databse.xlsx",     
                             sheet = "all")

#Create database with only studies for CTCA with filter
ct <- ct %>%
  filter(scan== "ctca") %>%
  drop_na(anyplaque_n_hiv)
#Drop d'abramo & duarte
ct <- ct[-c(3,6,9),]
#create labels
#remove et al. from data
ct$study<-gsub("et al.","",as.character(ct$study))
labs <- paste(ct$study, ct$year)

#set up data fram for proportion of PLHIV with LGE
ct <- ct %>% select(study, year, country, income, design, excludedcad, hivn_ct, anyplaque_n_hiv, cd4, age_hiv, excludedcad, stableart, qualityrating)



any.es <- escalc(xi = anyplaque_n_hiv, ni = hivn_ct, measure = "PLO", data = ct, slab= labs)
any.pes <- rma(yi, vi, data = any.es)

#write own transformation which is inverse of LOGIT * 100
mytransf <- function(x)
    (transf.ilogit(x)) * 100

par(mfrow=c(2,2))
forest(any.pes, transf = mytransf,
       mlab= "",
       digits = 1, header= TRUE,
       ilab = cbind(ct$anyplaque_n_hiv, ct$hivn_ct),
       ilab.xpos = c(-45,-25),
       xlim = c(-110, 150),
       xlab = "Prevalence of Coronary Plaque (%)",
       order = ct$year)

text(c(-45,-25), 14, c("Cases", "N"), cex=0.75)

## add text with Q-value, dfs, p-value, and I^2 statistic
text(-110, -1, pos=4, cex=0.75, bquote(paste("RE Model (Q = ",
     .(formatC(any.pes$QE, digits=2, format="f")), ",p = ", .(formatC(any.pes$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(any.pes$I2, digits=1, format="f")), "%)")))

mtext(c("A"), side = 3, line = 1)


```


# Risk of coronary plaque
```{r}

#new analysis using the correct database

# Load data with odds ratios
#Load excel file
or.any <- read_excel("hiv_sr_databse.xlsx",     
                             sheet = "all")

#Create database with only studies for CTCA with filter
or.any <- or.any %>%
  filter(scan== "ctca") %>%
  drop_na(anyplaque_n_hiv)


#Drop d'abramo & duarte
or.any <- or.any[-c(3,10),]



#set up data fram for proportion of PLHIV with LGE
or.any <- or.any %>% select(study, year, hivn_ct, anyplaque_n_hiv, controln_ct, anyplaque_n_con, or_any, pval_any, ci.lb_any, ci.ub_any, adjust)

or.any <- or.any %>% 
  drop_na(anyplaque_n_con)%>% #Drop studies with NA in control group
  mutate(
    hneg = (hivn_ct - anyplaque_n_hiv),
    cneg = (controln_ct - anyplaque_n_con)
  ) %>%
  rename(hpos = anyplaque_n_hiv, cpos = anyplaque_n_con, 
         hiv.n = hivn_ct, con.n = controln_ct, or = or_any, 
         pval = pval_any, ci.lb= ci.lb_any, ci.ub = ci.ub_any) %>%
  select(study, year, hiv.n, hpos, hneg, con.n, cpos, cneg, or, pval,
         ci.lb, ci.ub, adjust)

#Remove Lai 1
or.any[c(4), c(3:7)] <- NA

#create branch off df for labels
or.anylabs <- or.any

#remove values from df for escalc
or.any[c(2, 5,4, 7), c(3:8)] <- NA

#create labels
#remove et al. from data
or.any$study<-gsub("et al.","",as.character(or.any$study))
labs <- paste(or.any$study, or.any$year)

# Calcuate odds ratios using escalc 
es <- escalc(measure= "OR", ai = hpos, bi = hneg, ci = cpos,
              di = cneg, 
              slab= labs,
              data = or.any)

#Replace the missing values withthe log odds ratios 

es$yi <- replmiss(es$yi, log(es$or))
# Convert the p-values into z values
es$zi <- sign(es$yi) * qnorm(es$pval/2, lower.tail=FALSE)
# Test statistics can be converted to standard errors
es$sei <- es$yi / es$zi
# CI bounds can be converted to SE
es$sei <- replmiss(es$sei, with(es, (log(ci.ub) - log(ci.lb))/(2*1.96)))
# Missing values with the vi variable can be replaced
es$vi <- replmiss(es$vi, es$sei^2)
# Delete variables
es$zi <- es$sei <- NULL



pes <- rma(yi, vi, data = es)


# Forest plot of odds ratio
forest(pes,
       addpred=TRUE, header=TRUE,
       atransf=exp,
       order = or.any$year,
       xlim= c(10, -13),
      ilab=cbind(or.anylabs$hpos, or.anylabs$hneg, 
                 or.anylabs$cpos, or.anylabs$cneg),
       ilab.xpos=c(-7.3,-6.0,-4.3,-3.0),
      mlab = "",
      xlab = c("Odds Ratio"),
        at=log(c(0.1, .25, 1, 10, 30)))

#Add text to label columns
text(c(-7.3,-6.0,-4.3,-3.0), 11.5, c("Pos", "Neg", "Pos", "Neg"), cex=0.75)
text(c(-6.65, -3.65), 12.5, c("HIV+", "HIV-"), font =2, cex = 0.75)

## add text with Q-value, dfs, p-value, and I^2 statistic
text(-12.9, -1, pos=4, cex=0.75, bquote(paste("RE Model (Q = ",
     .(formatC(pes$QE, digits=2, format="f")), ", df = ", .(pes$k - pes$p),
     ", p = ", .(formatC(pes$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(pes$I2, digits=1, format="f")), "%)")))
mtext("B", side= 3, line= 1)
```

```{r}
# Sensitivity analysis with removal of papers that did not adjust.
dev.new()
# Remove abdel, fitch, li
pes2 <- rma(yi, vi, data=es, subset = (adjust == "yes"))
forest(pes2, addpred=TRUE, header=TRUE, atransf=exp, xlim= c(10,-13),
      ilab=cbind(or.anylabs$hpos, or.anylabs$hneg, 
                 or.anylabs$cpos, or.anylabs$cneg),
      ilab.xpos=c(-7.3,-6.0,-4.3,-3.0), mlab = "", xlab = c("Odds Ratio"), at=log(c(0.1, .25, 1, 10, 100)))

#Add text to label columns
text(c(-7.3,-6.0,-4.3,-3.0), 9.5, c("Pos", "Neg", "Pos", "Neg"), cex=0.75)
text(c(-6.65, -3.65), 10.5, c("PLHIV", "Controls"), font =2)

## add text with Q-value, dfs, p-value, and I^2 statistic
text(-12.9, -1, pos=4, cex=0.75, bquote(paste("RE Model (Q = ",
     .(formatC(res.2.sens$QE, digits=2, format="f")), ", df = ", .(res.2.sens$k - res.2.sens$p),
     ", p = ", .(formatC(res.2.sens$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(res.2.sens$I2, digits=1, format="f")), "%)")))
```

## Heterogeneity evaluation of prevalence of any coronary plaque
### CVD inclusion criteria
Sensitivity analysis excluding two studies that did not exclude patients with cardiovascular disease.
```{r, warning=FALSE, echo=FALSE}
# Presence of any coronary plaque based on whether study excluded patients with CVD
# This has to be a sensitivity analysis as only 2 studies did NOT exclude (Miller 15, Senoner 19)

#Create a subset of studies only EXCLUDING cvd
ctcvd <- subset(ct, excludedcad=="yes")
ctcvd <- ctcvd %>% drop_na(anyplaque_n_hiv)
#set up data fram for proportion of PLHIV with LGE
ctcvd <- ctcvd %>% select(study, year, country, income, design, excludedcad, hivn_ct, anyplaque_n_hiv, cd4, age_hiv, excludedcad, stableart, qualityrating)
#remove Lai, dabramo, duarte
ctcvd <- ctcvd[-c(3,6,8),]
#remove et al. from data
ctcvd$study<-gsub("et al.","",as.character(ctcvd$study))
labs <- paste(ctcvd$study, ctcvd$year)
ctcvd

any.es.cvd <- escalc(xi = anyplaque_n_hiv, ni = hivn_ct, measure = "PLO", data = ctcvd, slab= labs)
any.pes.cvd <- rma(yi, vi, data = any.es.cvd)

#write own transformation which is inverse of LOGIT * 100
mytransf <- function(x)
    (transf.ilogit(x)) * 100


forest(any.pes.cvd, transf = mytransf,
       mlab= "",
       digits = 1, header= TRUE,
       ilab = cbind(ctcvd$anyplaque_n_hiv, ctcvd$hivn_ct),
       ilab.xpos = c(-45,-25),
       xlim = c(-110, 150),
       xlab = "Prevalence of Coronary Plaque (%)",
       order = ctcvd$year)

text(c(-45,-25), 14, c("Cases", "N"), cex=0.75)

## add text with Q-value, dfs, p-value, and I^2 statistic
text(-110, -1, pos=4, cex=0.75, bquote(paste("RE Model (Q = ",
     .(formatC(any.pes.cvd$QE, digits=2, format="f")), ",p = ", .(formatC(any.pes.cvd$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(any.pes.cvd$I2, digits=1, format="f")), "%)")))




```


```{r, warning=FALSE, echo=FALSE}
anycvd <- metaprop(event = anyplaque_n_hiv, 
                   n = hivn_ct,
                   studlab = study,
                   data = ctcvd,
                   method = "Inverse",#Inverse variance method
                   sm = "PLOGIT", #Log transformation of proportions
                   random = TRUE,#random effects meta analysis
                   fixed = FALSE,
                   pscale = 100,
                   digits = 1)
forest(anycvd, 
            rightcols=FALSE,
            leftcols=c("studlab", "event", "n", "effect", "ci"),
            leftlabs = c("Study", "Cases", "Total", "Prevalence", "95% C.I."),
            xlim= c(0,110),
            xlab = c("Prevalence of any coronary plaque (%)"),
            smlab = "",
            digits = 1,
            squaresize = 1,
            weight.study = "fixed",
            sortvar = year,
            fontsize = 10,
            fs.hetstat = 9)
          
```




### Metaregressions

Meta regression of any coronary plaque against average age of the study population

```{r, warning=FALSE, echo=FALSE}
# Use metaprop to enable metaregressions. Repeat meta analysis of proportions using metaprop.


#Load excel file
ct1 <- read_excel("hiv_sr_databse.xlsx",     
                             sheet = "all")

#Create database with only studies for CTCA with filter
ct1 <- ct1 %>%
  filter(scan== "ctca") %>%
  drop_na(anyplaque_n_hiv)

#Drop d'abramo & duarte
ct1 <- ct1[-c(3,6,10),]
#create labels
#remove et al. from data
ct1$study<-gsub("et al.","",as.character(ct1$study))
labs <- paste(ct1$study, ct1$year)

#set up data fram for proportion of PLHIV with LGE
ct1 <- ct1 %>% select(study, year, country, income, design, excludedcad, hivn_ct, anyplaque_n_hiv, cd4, age_hiv, excludedcad, stableart, qualityrating, femalehivprop, bmihiv, smokehivprop, age_hiv, artprop, art_time, cd4, nadircd4)

ct1$cd4 <- as.numeric(ct1$cd4)
ct1$art_time <- as.numeric(ct1$art_time)
ct1$bmihiv <- as.numeric(ct1$bmihiv)

any <- metaprop(event = anyplaque_n_hiv, 
                   n = hivn_ct,
                   studlab = study,
                   data = ct1,
                   method = "Inverse",#Inverse variance method
                   sm = "PLOGIT", #Log transformation of proportions
                   random = TRUE,#random effects meta analysis
                   fixed = FALSE,
                   pscale = 100,
                   digits = 1)

anyage <- metareg(any, ~ age_hiv, hakn = TRUE, method = "DL",
                       digits = 2,
                  subset= c(1:11)) #remove lo et al. from meta regression

# Mixed effects model meta regression
anyfemale <- metareg(any, ~ femalehivprop,
                       hakn = TRUE,
                       method = "DL",
                       digits = 2)
# Meta regression of the proportion of smokers in the study population
# Not reported by: DETTORE
anysmoke <- metareg(any, ~ smokehivprop,
                       hakn = TRUE,
                       method = "DL",
                       digits = 2) 
# Meta regression of BMI of study population against any coronary plaque

anybmi <- metareg(any, bmihiv,
                       hakn = TRUE,
                       method = "DL",
                       digits = 2,
                  subset= c(1:11)) #remove lo et al. from meta regression)


anyart <- metareg(any, ~ artprop,
                       hakn = TRUE,
                       method = "DL",
                       digits = 2)

anytime <- metareg(any, ~ art_time,
                       hakn = TRUE,
                       method = "DL",
                       digits = 2,
                   subset= c(1:11)) #remove lo et al. from meta regression)


anycd4 <- metareg(any, ~ cd4,
                       hakn = TRUE,
                       method = "DL",
                       digits = 2,
                        subset= c(1:11)) #remove lo et al. from meta regression)

# Meta regression of coronary plaque by mean nadir CD4 in study population
# Not reported by Hoffman, Jeudy

anynadir <- metareg(any, ~ nadircd4,
                       hakn = TRUE,
                       method = "DL",
                       digits = 2,
                    subset= c(1:11)) #remove lo et al. from meta regression)



dev.new()
par(mfrow=c(4,2),oma=c(2,2,0,0))
regplot(anyage, 
        transf=mytransf, 
        main = "A",
        ylim = c(0,100),
        ylab = "",
        xlab = "Age (years)",
        ci= TRUE,
        label = FALSE,
        pi = FALSE)
regplot(anyfemale, 
        transf= mytransf, 
        main = "B",
        ylim = c(0,100),
        ylab = "",
        xlab = "Proportion of women in study population (%)",
        ci= TRUE,
        pi = FALSE)
regplot(anysmoke, 
        transf=mytransf, 
        main = "C",
        ylim = c(0,100),
        ylab = "",
        xlab = "Proportion of smokers in study population (%)",
        ci= TRUE,
        pi = FALSE)
regplot(anybmi, 
        transf= mytransf, 
        main = "D",
        ylim = c(0,100),
        ylab = "",
        xlab = "Mean BMI in study population (kg/m2)",
        ci= TRUE,
        pi = FALSE)
regplot(anyart, 
        transf= mytransf,
        main = "E",
        ylim = c(0,100),
        ylab = "",
        xlab = "Proportion of HIV+ on ART",
        ci= TRUE,
        pi = FALSE)
regplot(anytime, 
        transf=mytransf, 
        main = "F",
        ylim = c(0,100),
        ylab = "",
        xlab = "Mean duration on ART (years)",
        ci= TRUE,
        pi = FALSE)
regplot(anycd4, 
        transf= mytransf,
        main = "G",
        ylim = c(0,100),
        ylab = "",
        xlab = "Mean CD4 count (cells/microl)",
        ci= TRUE,
        pi = FALSE)
regplot(anynadir, 
        transf=mytransf, 
        main = "H",
        ylim = c(0,100),
        ylab = "",
        xlab = "Nadir CD4 count (cells/microl)",
        ci= TRUE,
        pi = FALSE)
mtext("Prevalence of coronary plaque (%)",side=2,line=0,outer=TRUE,las=0)
```


### Summary of Meta Regressions of any coronary plaque

```{r, echo=FALSE, warning=FALSE}
regresult <- tibble(
    Variable = c("Age", "Proportion female", "Proportion smokers", "Mean BMI", "Proportion on ART", "Time on ART", "Mean CD4", "Nadir CD4"),
    no.studies = c(anyage$k, anyfemale$k, anysmoke$k, anybmi$k, anyart$k, anytime$k, anycd4$k, anynadir$k),
    regression.coefficent = c(anyage$b[[2]], anyfemale$b[[2]], anysmoke$b[[2]], anybmi$b[[2]], anyart$b[[2]], anytime$b[[2]], anycd4$b[[2]], anynadir$b[[2]]),
    ci.lower = c(anyage$ci.lb[[2]], anyfemale$ci.lb[[2]], anysmoke$ci.lb[[2]], anybmi$ci.lb[[2]], anyart$ci.lb[[2]], anytime$ci.lb[[2]], anycd4$ci.lb[[2]], anynadir$ci.lb[[2]]),
    ci.upper = c(anyage$ci.ub[[2]], anyfemale$ci.ub[[2]], anysmoke$ci.ub[[2]], anybmi$ci.ub[[2]], anyart$ci.ub[[2]], anytime$ci.ub[[2]], anycd4$ci.ub[[2]], anynadir$ci.ub[[2]]),
    p.value = c(anyage$pval[[2]], anyfemale$pval[[2]], anysmoke$pval[[2]], anybmi$pval[[2]], anyart$pval[[2]], anytime$pval[[2]], anycd4$pval[[2]], anynadir$pval[[2]]),
    R2 = c(anyage$R2, anyfemale$R2, anysmoke$R2, anybmi$R2, anyart$R2, anytime$R2, anycd4$R2, anynadir$R2),
      )%>%
  mutate(across(where(is.numeric), round, digits = 2))
regresult <- regresult %>% flextable() %>%
  theme_vanilla()%>%
  set_header_labels(
    variable = "Variable",
    no.studies = "N studies",
    regression.coefficent = "Regression Coefficent",
    ci.lower = "95% CI lower",
    ci.upper = "95% CI upper",
    p.value = "P Value",
    R2 = "R Squared")
print(regresult, preview= "docx")

```

## Exploration of heterogeneity by study design

### Sensitivity analysis with studies of poor quality excluded
```{r, warning=FALSE, echo=FALSE}
#Updated meta estiamte with Frustaci removed and Breukman
#Create dataframe with poor quality studies removed
ctqual <-  ctany %>% 
  filter(quality != "poor")   

qual <- metaprop(event = anyplaque_n_hiv, 
                   n = hivn_ct,
                   studlab = study,
                   data = ctqual,
                   method = "Inverse",#Inverse variance method
                   sm = "PLOGIT", #Log transformation of proportions
                   random = TRUE,#random effects meta analysis
                   fixed = FALSE,
                   pscale = 100,
                   digits = 1)
forest(qual, 
            rightcols=FALSE,
            leftcols=c("studlab", "event", "n", "effect", "ci"),
            leftlabs = c("Study", "Cases", "Total", "Prevalence", "95% C.I."),
            xlim= c(0,110),
            smlab = "",
       xlab = c("Prevalence of any coronary plaque (%)"),
            digits = 1,
            squaresize = 1,
            weight.study = "fixed",
            sortvar = year,
            fontsize = 10,
            fs.hetstat = 9)
```

# 50/70% Stenosis Analysis
## 50% stenosis prevalence
```{r, warning=FALSE, echo = FALSE}
#Create database with only studies for CTCA with filter
#Load excel file
ct <- read_excel("hiv_sr_databse.xlsx",     
                             sheet = "all")

ct50 <- ct %>%
  filter(scan== "ctca") %>%
  drop_na(stenhiv50n)

# Remove lai et al. 
ct50 <- ct50[-c(7),]

#create labels
#remove et al. from data
ct50$study<-gsub("et al.","",as.character(ct50$study))
labs <- paste(ct50$study, ct50$year)

#set up data fram for proportion of PLHIV with LGE
ct50 <- ct50 %>% select(study, year, country, income, design, excludedcad, hivn_ct, stenhiv50n, controln_ct,stencon50n,  cd4, age_hiv, excludedcad, stableart)

#replaace hoffman denominator 755 to 743
ct50[6,7] <- 743

sten.es <- escalc(xi = stenhiv50n, ni = hivn_ct, measure = "PLO", data = ct50, slab= labs)
sten.pes <- rma(yi, vi, data = sten.es)

#write own transformation which is inverse of LOGIT * 100
mytransf <- function(x)
    (transf.ilogit(x)) * 100


forest(sten.pes, transf = mytransf,
       mlab= "",
       at = c(0,20,40,60,80,100),
       digits = 1, header= TRUE,
       ilab = cbind(ct50$stenhiv50n, ct50$hivn_ct),
       ilab.xpos = c(-45,-25),
       xlim = c(-110, 150),
       xlab = "Prevalence of coronary stenosis (%)",
       order = ct50$year)


## add text with Q-value, dfs, p-value, and I^2 statistic
text(-110, -1, pos=4, cex=0.75, bquote(paste("RE Model (Q = ",
     .(formatC(sten.pes$QE, digits=2, format="f")), ",p = ", .(formatC(sten.pes$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(sten.pes$I2, digits=1, format="f")), "%)")))
text(c(-45,-25), 17, c("Cases", "N"), cex=0.75)
mtext("C", side = 3, line = 1)
```

## Risk of 50% stenosis

```{r}
# Load data with odds ratios
#Load excel file
orf <- read_excel("hiv_sr_databse.xlsx",     
                             sheet = "all")

#Create database with only studies for CTCA with filter
orf <- orf %>%
  filter(scan== "ctca")%>%
  drop_na(stencon50n)%>%
  select(study, year, hivn_ct, stenhiv50n, 
         controln_ct, stencon50n, or_sten, pval_sten, 
         ci.lb_sten, ci.ub_sten, adjust)%>%
  mutate(
    hneg = (hivn_ct - stenhiv50n),
    cneg = (controln_ct - stencon50n)) %>%
  rename(hpos = stenhiv50n, cpos = stencon50n, 
         hiv.n = hivn_ct, con.n = controln_ct, or = or_sten, 
         pval = pval_sten, ci.lb= ci.lb_sten, ci.ub = ci.ub_sten)%>%
  select(study, year, hpos, hneg, hiv.n, cpos, cneg, con.n, or, pval, ci.lb, ci.ub)

#remove et al. from data
orf$study<-gsub("et al.","",as.character(orf$study))
labs <- paste(orf$study, orf$year)

# Remove Lai numbers
orf[c(5), c(3:8)] <- NA
# Creat label databse
orflabs <- orf
#remove Post numbers
orf[c(6), c(3:8)] <- NA



# Calcuate odds ratios using escalc 
es.50 <- escalc(measure= "OR", ai = hpos, bi = hneg, ci = cpos,
              di = cneg, 
              slab= labs,
              data = orf)

#Replace the missing values withthe log odds ratios 

es.50$yi <- replmiss(es.50$yi, log(es.50$or))
# Convert the p-values into z values
es.50$zi <- sign(es.50$yi) * qnorm(es.50$pval/2, lower.tail=FALSE)
# Test statistics can be converted to standard errors
es.50$sei <- es.50$yi / es.50$zi
# CI bounds can be converted to SE
es.50$sei <- replmiss(es.50$sei, with(es.50, (log(ci.ub) - log(ci.lb))/(2*1.96)))
# Missing values with the vi variable can be replaced
es.50$vi <- replmiss(es.50$vi, es.50$sei^2)
# Delete variables
es.50$zi <- es.50$sei <- NULL



pes.50 <- rma(yi, vi, data = es.50)


# Forest plot of odds ratio
forest(pes.50,
       addpred=TRUE, header=TRUE,
       atransf=exp,
       order = orf$year,
       xlim= c(10, -13),
      ilab=cbind(orflabs$hpos, orflabs$hneg, 
                 orflabs$cpos, orflabs$cneg),
       ilab.xpos=c(-7.3,-6.0,-4.3,-3.0),
      mlab = "",
      xlab = c("Odds Ratio"),
        at=log(c(0.1, .25, 1, 10, 30)))

#Add text to label columns
text(c(-7.3,-6.0,-4.3,-3.0), 12.5, c("Pos", "Neg", "Pos", "Neg"), cex=0.75)
text(c(-6.65, -3.65), 13.5, c("HIV+", "HIV-"), font =2, cex = 0.75)

## add text with Q-value, dfs, p-value, and I^2 statistic
text(-12.9, -1, pos=4, cex=0.75, bquote(paste("RE Model (Q = ",
     .(formatC(pes.50$QE, digits=2, format="f")), ", df = ", .(pes.50$k - pes.50$p),
     ", p = ", .(formatC(pes.50$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(pes.50$I2, digits=1, format="f")), "%)")))
mtext("D", side= 3, line= 1)
```



```{r, warning=FALSE, echo = FALSE}
#Perform sensitivity analysis with studies that did not adjust removed.
# Remove: abdelmoniem, fitch, 

res3sens <- rma(yi, vi, data = es.50, subset = (adjust == "yes"))

forest(res3sens,
       addpred=TRUE, header=TRUE,
       atransf=exp,
       xlim= c(10, -13),
      ilab=cbind(or50$hivpos, or50$hivneg, 
                 or50$conpos, or50$conneg),
       ilab.xpos=c(-7.3,-6.0,-4.3,-3.0),
      mlab = "",
      xlab = c("Odds Ratio"),
        at=log(c(0.1, .25, 1, 10, 100)))

#Add text to label columns
text(c(-7.3,-6.0,-4.3,-3.0), 9.5, c("Pos", "Neg", "Pos", "Neg"), cex=0.75)
text(c(-6.65, -3.65), 10.3, c("PLHIV", "Controls"), font =2)

## add text with Q-value, dfs, p-value, and I^2 statistic
text(-12.9, -1, pos=4, cex=0.75, bquote(paste("RE Model (Q = ",
     .(formatC(res3sens$QE, digits=2, format="f")), ", df = ", .(res3sens$k - res3sens$p),
     ", p = ", .(formatC(res3sens$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(res3sens$I2, digits=1, format="f")), "%)")))
```


```{r, warning=FALSE, echo = FALSE}
# Remove Senoner ett al.
res3sens2 <- rma(yi, vi, data = or.50, subset = c(2:3, 5:6, 8:10))
predict(res3sens2, transf = exp)
forest(res3sens2,
       addpred=TRUE, header=TRUE,
       atransf=exp,
       xlim= c(10, -13),
      ilab=cbind(or50$hivpos, or50$hivneg, 
                 or50$conpos, or50$conneg),
       ilab.xpos=c(-7.3,-6.0,-4.3,-3.0),
      mlab = "",
      xlab = c("Odds Ratio"),
        at=log(c(0.1, .25, 1, 10, 100)))
## add text with Q-value, dfs, p-value, and I^2 statistic
text(-12.9, -1, pos=4, cex=0.75, bquote(paste("RE Model (Q = ",
     .(formatC(res3sens2$QE, digits=2, format="f")), ", df = ", .(res3sens2$k - res3sens2$p),
     ", p = ", .(formatC(res3sens2$QEp, digits=2, format="f")), "; ", I^2, " = ",
     .(formatC(res3sens2$I2, digits=1, format="f")), "%)")))

```


# Funnell Plots CTCA
```{r}

funnel(any.pes, atransf = mytransf, xlab = "Prevalence of coronary plaque (%)", digits = 1)
mtext("B", side =3, line = 1)
regtest(any.pes, model="lm", predictor="sei", digits = 1)

```
